### 2017-02-08 doc/manuscript.Rmd
Minor edits to TODO and manuscript

---
bibliography: 
    - /home/luke/Documents/bibliography/bib/bib-db/tagDiabetes.bib
    - /home/luke/Documents/bibliography/bib/bib-db/myrefs.bib
    - /home/luke/Documents/bibliography/bib/bib-db/methods.bib
csl: /home/luke/Documents/bibliography/styles/dependent/diabetes-care.csl
output: fost::default_manuscript
---

@@

Both clinically-measured TAG and total TAGFA concentration had very strong
negative associations with all outcome variables. While there were a few
significant interactions by time in unadjusted models, after inclusion of
covariates in the model, these interactions were attenuated (data not
shown). There were no significant interactions by sex or ethnicity for any of
the TAGFA (data not shown). We ran sensitivity analyses to identify which
covariate attenuated the beta-cell function associations from the unadjusted
model. We found that including waist circumference in the model lead to the
attenuation of associations, shown in `r cite_st("gee_adj_nowaist")`. A tabular
presentation of the GEE results is shown in `r cite_st("gee_unadj")` for
unadjusted models and `r cite_st("gee_adj")` for adjusted models.

>>>>

---
bibliography: 
    - /home/luke/Documents/bibliography/bib/bib-db/tagDiabetes.bib
    - /home/luke/Documents/bibliography/bib/bib-db/myrefs.bib
    - /home/luke/Documents/bibliography/bib/bib-db/methods.bib
csl: /home/luke/Documents/bibliography/styles/dependent/diabetes-care.csl
output: fost::diabetologia_manuscript
---

@@

Both clinically-measured TAG and total TAGFA concentration had very strong
negative associations with all outcome variables. While there were a few
significant interactions by time in unadjusted models, after inclusion of
covariates in the model, these interactions were attenuated (data not
shown). There were no significant interactions by sex or ethnicity for any of
the TAGFA (data not shown). We ran sensitivity analyses to identify which
covariate attenuated the beta-cell function associations from the unadjusted
model. We found that including waist circumference in the model lead to the
attenuation of associations, shown in `r cite_sf("gee_adj_nowaist")`. A tabular
presentation of the GEE results is shown in `r cite_st("gee_unadj")` for
unadjusted models and `r cite_st("gee_adj")` for adjusted models.
